Improving the Image Acquisition Rate of an Atomic Force Microscope Through Compressive Sampling

### 2019-06-12 latex/afm-cs-main.tex
Update on Overleaf.
Update figures.

\maketitle
\begin{abstract}
  Undersampling-based approaches in Atomic Force Microscopy (AFM) aim to reduce
  the time to acquire an image by reducing the number of measurements needed
  while still maintaining image quality. In this paper, we describe a hardware
  implementation and demonstration of one such approach based on the use of
  collections of short scans known as $\mu$--paths. Using a commercial AFM, we
  acquire data on a grating sample.
  %using two different sampling
  %approaches: randomly-placed $\mu-$paths and $\mu-$paths designed to minimize
  %the reconstruction error based on partial prior information about the spatial
  %frequency content in the sample image.
  Reconstructions are made from these data using
  %three approaches: (1) inpainting, an interpolation technique that
  %diffuses information from sampled locations into unsampled regions, (2)
  %basis-pursuit, a compressive sensing-based algorithm that seeks to minimize a
  %measure of sparsity in the underlying image, and (3)
  a new variant of basis
  pursuit, Basis Pursuit with Vertical Variation (BPVV), that is designed to reduce
  artifacts arising from the sampling pattern. The quality of the resulting
  images is compared to images from standard raster scans of the same regions at
  comparable imaging rates using both the peak signal-to-noise ratio and the
  structured similarity index metric
  and a new metric we call the relative damage index.
  \todo{Will this conclusion still hold?}
  These experiments demonstrate that at slow
  scan rates, the $\mu-$path scheme produces similar image quality with
  significantly less sampling (and thus less tip-sample interaction) and that at
  high rates, the undersampling scheme produces higher quality images than
  raster scanning.
\end{abstract}

@@

Our previous work on the $\mu$-path pattern using theoretical calculations,
simulations, and a preliminary implementation, demonstrates that the approach
can achieve significant scanning time reduction while maintaining faithful image
reconstruction \cite{maxwell2014compressed,Luo:2015tu, braker_hardware_2018}. This paper
builds upon that earlier work in several significant ways.
% % ------------------ TKTKTKT ------------------
% \todo{Strike this?}
% First, we demonstrate
% performance using both randomly-placed $\mu-$paths and designed $\mu-$paths that
% are optimized to minimize the expected reconstruction error given some initial
% estimate of the frequency structure of the sample. These schemes are described
% in Sec. \ref{sec:samplingScheme}.
% % --------------------------
We also introduce a new reconstruction
algorithm which is designed to minimize the artifacts arising from the structure
of the $\mu$-path scanning pattern. This algorithm is described and compared to
existing reconstruction methods through simulations in Sec.
\ref{sec:reconstructionMethods}.
Section \ref{sec:control} describes improvements to the control algorithms compared to our preliminary implementation in ~\cite{braker_hardware_2018}.
We then demonstrate the entire scheme from
sampling through reconstruction using experiments on a commercial AFM (Agilent
5500). The experimental setup and implementation details are described in Secs.
\ref{sec:experimentalSetup} and \ref{sec:implementation}\footnote{The software
  portion of the implementation and image reconstruction described in this paper
  can be found at \url{https://github.com/rabraker/AFM_CS}}. Experimental results are provided in Sec.
\ref{sec:results}. Finally, we provide a few concluding remarks in
Sec. \ref{sec:conclusions}.

@@

In the AFM application, the probe can only measure a single pixel at a time.
Thus the rows of $R$ are a subset of the rows of an $m$ by $m$ identity matrix.
Ideally, the sparsity basis and
the measurement matrix $R$ will have a low \textit{mutual coherence}, a
measure that describes how each of the rows of $R$ (the measurements)
``spreads out'' in the domain of $U$ \cite{candes2007sparsity}.
In the following, we assume that $U^TU=I$, though in the simulation and
experimental results, we take $U$ as the Discrete Cosine Transform (DCT) basis.
The DCT basis generally keeps a good balance between achieving a low
mutual coherence between $U$ and the required structure of the AFM sensing
matrices $R$ and providing a high sparsity of typical AFM sample images.

@@

\todo{This development is way too long!}
To mitigate these affects, we propose a new variant of BPDN that we term basis pursuit with
vertical variation (BPVV). BPVV adds a vertical total variation penalty in the spatial domain to the
optimization objective. That is, \eqref{op:bp} is modified to
\todo{It has been my observation that some benefit is gained by including $D_h$, but weighting it less than $D_v$. Not sure if we should leave it in. If so, BPVV should be BPTV or something.}
\begin{align}
  \min_{x\in Q_p}~f(x) &= \min_{x\in Q_p} \left\|U^Tx\right\|_1
                         + \alpha\left\|D_vx\right\|_1
                         + \beta\left\|D_hx\right\|_1 \label{op:bp_tv}\\
                       &=\min_{x\in Q_p} \left\|Wx\right\|_1 \label{op:bp_tvW}
                         % \quad W = \begin{bmatrix}U&\alpha_hD^T_h&\alpha_vD^T_v \end{bmatrix}^T \nonumber
\end{align}
where
\begin{equation*}
W = \begin{bmatrix}U&\alpha_hD^T_h&\alpha_vD^T_v \end{bmatrix}^T
\end{equation*}
with ${D_v x=\text{vec}(\nabla_v X)}$ (resp., ${D_v x=\text{vec}(\nabla_v X)}$) representing a 
discrete gradient of a matrix in the vertical (resp., horizontal) direction (see, e.g., \cite[Section 6.1,]{becker_nesta_2011}). 
% and
% \begin{align*}
%   (\nabla_v X)_{i,j} = 
%   \begin{cases}
%     X_{i+1,j} - X_{i,j}, & 1\leq i<h,~ 1\leq j\leq s,\\
%     0, & \phantom{:}i=h,~\phantom{:::::} 1\leq j\leq s.
%   \end{cases}\\
%   (\nabla_h X)_{i,j} = 
%   \begin{cases}
%     X_{i,j+1} - X_{i,j}, & 1\leq i\leq h,~1\leq j<s \\
%     0, & \phantom{}1\leq i\leq,~\phantom{:::} j=s
%   \end{cases}
% \end{align*}
Thus, in \eqref{op:bp_tv}, $\left \| D_v x \right \|_1$ (resp., $\left \| D_h x \right \|_1$) is the total variation (TV) of the signal in the vertical (resp., horizontal) direction.
The parameters $\alpha$ and $\beta$ are weighting parameters.
The description of BPVV in \eqref{op:bp_tvW} can be interpreted as changing our assumption of sparsity in the DCT basis to assuming sparsity in an overcomplete dictionary \cite{candes_redundant_2011}.
\todo{I believe this is correct: Sean/Yufan can you confirm or reject?}

Moreover, when written as \eqref{op:bp_tvW}, the problem is in a form that may be solved with NESTA~\cite{becker_nesta_2011}. For completeness, we give an overview here.
To that end, we re-write the cost $f(x)$ in \eqref{op:bp_tvW} as
\begin{equation*}
  f(x) = \max_{u\in Q_d} \left\langle u, Wx \right\rangle,\quad Q_d = \{u:~||u||_{\infty} \leq 1\}.
\end{equation*}

One of the core features of the NESTA algorithm is to replace the non-smooth functional $f(x)$ with a smoothed approximation
\begin{equation}
  f_{\mu} = \max_{u\in Q_d} \left\langle u,
    W x \right\rangle - \frac{\mu}{2}||u||_2^2. \label{eqn:fcn_prox}
\end{equation}
The gradient of \eqref{eqn:fcn_prox} is given by
\begin{equation*}
  \nabla f_{\mu}(x)[i] = W^Tu_{\mu}(x)
\end{equation*}
where
\begin{equation*}
  (u_{\mu}(x))[i] = 
\begin{cases}
    \mu^{-1}(Wx)[i], & |W x[i]| < \mu,\\
    \text{sgn}(W x[i]), & \text{else}.
  \end{cases}
\end{equation*}
The optimization \eqref{op:bp_tv} may now be solved using Algorithm~\ref{ag:NESTA}.

\begin{algorithm}
  \SetKwInOut{Initialize}{Initialize} \SetKwInOut{Output}{Output}

  \Initialize{$x \in Q_p, \mu=0.9||W x_0||_{\infty}$, $L_{\mu} = \frac{1}{\mu}||W||^2_2$}
    % $x^{k+1} = x^{k}$\\
  \While{$\mu < \mu_{\textrm{final}}$ } {
    $k=0$\\
      \While{$\Delta f_{\mu} > \delta$} {
        $\alpha_k = \frac{1}{2}(k+1)$ \\
        $\tau_k = \frac{2}{k+3}$ \\
        $\displaystyle y_k = \text{arg } \min_{x\in Q_p}
          \frac{L_{\mu}}{2}||x - x_k||_2^2 + \langle \nabla f(x_k),~ x\rangle$\\
        $\displaystyle {z_k = \text{arg } \min_{x\in Q_p} \frac{L_{\mu}}{2}||x-x_0||_2^2 +
        \langle \sum_{i=0}^k \alpha_i \nabla f(x_i), ~x \rangle}$\\
        $x_{k+1} = \tau_kz_k + (1-\tau_k)y_k$\\
        $k \leftarrow k + 1$\\
      }
      $x_0 = x_k$\\
      $\mu = \gamma \mu$\\
      $L_{\mu} = (1/\mu)||W||^2_2$
    }
  \Output{Reconstruction $x_k$}
  \caption{NESTA algorithm}
  \label{ag:NESTA}
\end{algorithm}
  \todo{seems like a waste of space to reprint the algo, since its really no different than the reference}

In the termination condition for the inner loop, $\Delta f_{\mu} = |f_{\mu}(x_k) - \bar{f}_{\mu}(x_k)|/\bar{f}_{\mu}(x_k)$ where
\begin{equation}
\bar{f}_{\mu}(x_k) = \frac{1}{\min\{10, k\}} \sum_{\ell=1}^{\min\{10,k\}} f_{\mu}(x_{k-\ell})
\end{equation}
When $RR^T=I$, the sub-problems in lines 6 and 7 have a closed-form solution. Details can be found in~\cite{becker_nesta_2011}.

% The sub-problems in lines 6 and 7 have the form
% \begin{equation}
%   p = \textrm{arg } \min_{x\in Q_p} \frac{L}{2}||x - r|| + \langle g,~x - r\rangle
% \end{equation}
% for some vectors $g$ and $r$ and, as shown in~\cite{becker_nesta_2011}, have a closed-form solution given by
% \begin{align}
%   \lambda & = \textrm{max}(0, \sigma^{-1}\left| b - Rq\right| - L\\
%   q &= r - L^{-1}g\\
%   p &= \left(I - \frac{\lambda}{\lambda + L} R^TR\right)\left( \frac{\lambda}{L}R^Tb + q\right).
% \end{align}

@@

% =========================================================================
\section{Control}\label{sec:control}
The control structure for each axis is similar and essentially consists of a set of filters in series with a PI controller. The open-loop frequency response for the $Z$-axis is shown in Fig.~\ref{fig:z_control} (black curve) and in Fig.~\ref{fig:mimo_frf_uxuy} for the $X$ and $Y$ axes (red curves). The first resonance of each axis is the bending mode. For the $Z$ axis, this resonance is at 215~Hz and at approximately 350~Hz for the $X$ and $Y$ axes.

@@

% One challenge to the inversion approach is both the system gain and resonance at 215~Hz
% changes not only day-to-day but also (and especially) when changing cantilevers and our inversion is not robust to this. However, because $D^{-1}$ is defined purely by a second order fit to a small band of the FRF, updating the compensator can be automated.
% \todo{What else to say here?}

\begin{figure}[t!]
  \centering
  \includesvg[width=1\columnwidth]{figures/z_control_design.svg}
  \caption{FRFs of the $Z$-axis. The blue curve is the open loop response from $u_Z$ to deflection. By inverting the bending mode at 215~Hz, we achieve the black curve in closed-loop.}
  \label{fig:z_control}
\end{figure}

@@

\begin{figure*}[t]
  \centering
  \includegraphics[width=0.75\textwidth]{figures/AFM_loop_z.pdf}
  \caption{Block diagram of the $Z$-axis control loop. The anti-windup is active
    for decision index $i\in\{0,1,5\}$, which correspond to states such that
    $r_Z=\rzup$.}
  \label{fig:afm_bd_dinv}
\end{figure*}

% One cause for such different gains is variation in the length of the cantilever
% (and possibly how the laser was adjusted). This is illustrated in
% Fig.~\ref{fig:z_axis_gain}. Here, we consider a cantilever with length $h$ that
% rests on the surface of some specimen with a nominal angle of $\theta$. In this
% drawing, the laser is perpendicular to the sample surface. Given a vertical
% perturbation $\Delta z$, we have that
% \begin{equation}
%   \Delta \alpha \approx \frac{d}{h} \Delta z,
% \end{equation}
% where $d$ is the distance from the cantilever to the detector and
% $\Delta \alpha$ is the change in position of the incident laser spot on the
% detector. Thus, given the same change in the vertical position, we will see a
% larger change in the deflection signal for a shorter cantilever. In other words,
% a short cantilever will exhibit a larger DC-gain in the $G_{u_Z,Z_d}$ transfer
% function.
% \begin{figure}
%   \begin{minipage}[t]{.46\textwidth}
%     % L B R T
%     \includesvg[width=1\textwidth]{figures/z_cant_evolution.svg}
%     \caption{FRFs of three different cantilevers, showing substantial
%       differences in the DC-gain and smaller, but still significant differences
%       the frequency of the modes.}
%     \label{fig:z_evolution}
%   \end{minipage}
%   \hfill
%   \begin{minipage}[t]{.46\textwidth}
%     % L B R T
%     \includegraphics[width=1\textwidth]{figures/z_axis_gain_schematic-crop.pdf}
%     \caption{Schematic drawing of how the length of the cantilever affects the
%       $z$-axis gain.}
%     \label{fig:z_axis_gain}
%   \end{minipage}
% \end{figure}

% Fig.~\ref{fig:z_evolution} shows the frequency response of $G_{u_Z,Z_d}$ near
% the bending mode for three different cantilevers. Cantilevers (A) and (B) are
% both AppNano SICON cantilevers and have a nominal length of 450 microns.
% Cantilever (C) is an NCLR and has a nominal length of 225 microns.
% Interestingly, the SICON cantilevers show substantial variation. Unfortunately,
% the manufacture does not provide a tolerance on the nominal length, so it is
% difficult to tease out whether that variation is due to manufacturing
% variability or other factors not explained by this analysis.

% Notably, the frequency of the pole and zero do appear to shift and our inversion
% scheme is not robust to this. To deal with this, I have built a (mostly)
% automated system ID routine into the imaging software. This routine is a
% specialized version of the techniques described previously in
% Chapter~\ref{chap:modeling}. First, it obtains an FRF of the bending mode over a
% frequency range spanning 180~Hz to 240~Hz (the same set of points as in
% Fig.~\ref{fig:z_evolution}). The input and output sinusoids are demodulated in
% quasi-realtime as they come off the FPGA. Once this is complete, a 2-pole,
% 2-zero transfer function model of the form
% \begin{equation*}
%   \hat{D}(z) = k \frac{z^2 + b_1z + b_o}{z^2 + a_1z + a_o}
% \end{equation*}
% is fit to the FRF, using the same optimization scheme as \eqref{eqn:logfit}.
% This is done inside the LabView VI by calling a custom DLL, which leverages
% CMPFIT~\cite{cmpfit,markwardt_mpfit_2009}, a
% Levenberg-Marquardt~\cite{more_levenberg_1978} routine written in C. To promote
% a stable fit, the optimization enforces the necessary conditions that
% \begin{align*}
%   |a_1| &< 2, \quad  |a_o| < 1\\
%   |b_1| &< 2, \quad  |b_o| < 1.
% \end{align*}
% The routine then checks that both the poles and zeros are indeed stabile, saves
% the data to a JSON file and passes the transfer function parameters into the
% imaging portion of the application which finally uploads the parameters into the
% FPGA imaging bitfile. Optionally, one can by-pass this step and simply load the
% previously saved JSON file.

% One of the benefits of this approach is that the DC-gain of the transfer
% function $G_{u_Z,Z_d}$ becomes (approximately) normalized to unity, which makes
% re-tuning the control system after changing tips far easier to non-existent. The
% benefit to automating the process is that it drastically reduces the friction
% required to obtain an up-to-date compensator, which means that an up-to-date
% compensator is more likely to be used~\cite{abramovitch_25years_2015}.

% Fig.~\ref{fig:afm_bd_dinv} shows a block diagram if the $Z$-axis control loop.
% We point out a small change from Chapter~\ref{chap:cs_init}: the addition of
% $D^{-1}(z)$ changes the correct signal to use to represent the sample surface.
% If we take the output of the entire compensator, $u_Z=D_ID^{-1}e_z$, then we
% will get a lot of wiggles in the resulting signal. Rather, we need to take only
% the output of the integrator to represent the surface.
% % \begin{figure}
% %   \centering
% %   \includegraphics[width=1\columnwidth]{figures/AFM_loop_Dinv-crop.pdf}
% %   \caption{Block diagram of the $Z$-axis control loop with the inverse
% %   compensator. }
% %   \label{fig:afm_bd_dinv}
% % \end{figure}
% \begin{figure*}[t]
%   \centering
%   \includegraphics[width=0.75\textwidth]{figures/AFM_loop_Dinv_antiwup-crop.pdf}
%   \caption{Block diagram of the $Z$-axis control loop. The anti-windup is active
%     for decision index $i\in\{0,1,5\}$, which correspond to states such that
%     $r_Z=r_{Z,\textrm{up}}$.}
%   \label{fig:afm_bd_dinv_final}
% \end{figure*}

% It should be noted that this control is sufficient to eliminate the limit-cycle
% behavior described in Section~\ref{sec:aproachspeed}:

% % \begin{figure}[tbhp!]
% %   \centering\includegraphics[width=3.0in]{figures-SBA/uz_multiplexer_KI_anderssonLab2}
% %   \caption{The $z$-piezo movement is driven by switching between feedback from
% %   the $z$-axis position signal and from the deflection signal. The shaded area
% %   represents the digital control system, while the non-shaded region is the
% %   physical system.}
% %   \label{fig:zMultiplex_anderssonLab}
% % \end{figure}

@@

For raster scanning, we use a truncated Fourier series, where each Fourier coefficient is scaled by the inverse of the closed-loop FRF at the corresponding frequency. We truncate this series such that the highest frequency is smaller than 200 Hz. See, e.g., \cite{clayton_review_2009} for more details on this strategy. Note that this scheme implies that the effective bandwidth of the $X$-axis controller is higher while raster scanning than while CS-scanning. On the other hand, it also implies that the for faster scan rates, fewer Fourier coefficients are used, and so the approximation to a triangle wave is worse.

% =========================================================================
\subsection{State machine}
Implementing the $\mu$-path scheme involves operating the AFM in several
distinct stages. In the $xy$-direction, the system must transition from tracking
a step command (in the transition to a new measurement location) to tracking a
scan pattern. For our simple integral controller, this only involves changing
the reference signals $x_{ref}$ and $y_{ref}$.
In the $z$-direction, the system
must transition between tip descent, surface scanning, tip retraction, and
maintaining a $z$-axis position.

\subsection{The pre-scan}
\begin{figure*}
  \begin{subfigure}{.33\textwidth}
    \includesvg[width=1\textwidth]{figures/zbounce_uz_example.svg}
    \caption{ }
    % \label{fig: }
  \end{subfigure}
  \begin{subfigure}{.33\textwidth}
    \includesvg[width=1\textwidth]{figures/prescan_uz_example.svg}
    \caption{ }
    \label{fig:uz_prescan}
  \end{subfigure}
  \begin{subfigure}{.33\textwidth}
    \includesvg[width=1\textwidth]{figures/prescan_zbounce_PSD.svg}
    \caption{ }
    % \label{fig: }
  \end{subfigure}
  \caption{(a) A ``$Z$-bounce'' experiment where the $XY$-stage is motionless
    and the cantilever is repeatedly engaged and disengaged. (b) One cycle of a
    tightly packed set of CS-cycles where the movement between each measurement
    location is 0. (c) PSDs from the portions of the trajectories which are
    colored blue and turquoise, averaged over many such cycles, demonstrating
    that the scan process itself reduces vibration in the $Z$-axis.}
  \label{fig:prescan_difference}
\end{figure*}
After the tip-descent, we begin scanning in a ``pre-scan'' phase (state (3)).
During this phase,

% \section{Post-processing}\label{sec:post_process}
% Here, we discuss how we post-process the raster and CS images.

% Unfortunately, the mis-alignment is not simply constant offset, but rather
% drifts over time. This can be seen, e.g., in Fig.~\ref{fig:rast_aligned_0p5}.
% Thus, while the technique described here mitigates the issue, it does not fully
% eliminate the problem.

@@

\begin{figure*}[t!]
  \includesvg[width=1\textwidth]{figures/cs_raster_pixel_rows_6-5-2019.svg}
  \caption{Rows of pixels, as indicated by the red lines in
    Fig.~\ref{fig:resultsF1_images}. For clarity, not all images are included.}
  \label{fig:pixel_rows}
\end{figure*}

>>>>

\maketitle
\begin{abstract}
  Undersampling-based approaches in Atomic Force Microscopy (AFM) aim to reduce
  the time to acquire an image by reducing the number of measurements needed
  while still maintaining image quality. In this paper, we describe a hardware
  implementation and demonstration of one such approach based on the use of
  collections of short scans known as $\mu$--paths. Using a commercial AFM, we
  acquire data on a grating sample.
  %using two different sampling
  %approaches: randomly-placed $\mu-$paths and $\mu-$paths designed to minimize
  %the reconstruction error based on partial prior information about the spatial
  %frequency content in the sample image.
  Reconstructions are made from these data using
  %three approaches: (1) inpainting, an interpolation technique that
  %diffuses information from sampled locations into unsampled regions, (2)
  %basis-pursuit, a compressive sensing-based algorithm that seeks to minimize a
  %measure of sparsity in the underlying image, and (3)
  a new variant of basis
  pursuit, Basis Pursuit with Vertical Variation (BPVV), that is designed to reduce
  artifacts arising from the sampling pattern. The quality of the resulting
  images is compared to images from standard raster scans of the same regions at
  comparable imaging rates using both the peak signal-to-noise ratio and the
  structured similarity index metric
  and a new metric we call the relative damage index.
  \todo{Re-write abstract, especially conclusions}
  These experiments demonstrate that at slow
  scan rates, the $\mu-$path scheme produces similar image quality with
  significantly less sampling (and thus less tip-sample interaction) and that at
  high rates, the undersampling scheme produces higher quality images than
  raster scanning.
\end{abstract}

@@

Our previous work on the $\mu$-path pattern using theoretical calculations,
simulations, and a preliminary implementation, demonstrates that the approach
can achieve significant scanning time reduction while maintaining faithful image
reconstruction \cite{maxwell2014compressed,Luo:2015tu, braker_hardware_2018}. This paper
builds upon that earlier work in several significant ways.

% % ------------------ TKTKTKT ------------------
% \todo{Strike this?}
% First, we demonstrate
% performance using both randomly-placed $\mu-$paths and designed $\mu-$paths that
% are optimized to minimize the expected reconstruction error given some initial
% estimate of the frequency structure of the sample. These schemes are described
% in Sec. \ref{sec:samplingScheme}.
% % --------------------------
We also introduce a new reconstruction
algorithm which is designed to minimize the artifacts arising from the structure
of the $\mu$-path scanning pattern. This algorithm is described and compared to
existing reconstruction methods through simulations in Sec.
\ref{sec:reconstructionMethods}.
Section \ref{sec:control} describes improvements to the control algorithms compared to our preliminary implementation in ~\cite{braker_hardware_2018}.
We then demonstrate the entire scheme from
sampling through reconstruction using experiments on a commercial AFM (Agilent
5500). The experimental setup and implementation details are described in Secs.
\ref{sec:experimentalSetup} and \ref{sec:implementation}\footnote{The software
  portion of the implementation and image reconstruction described in this paper
  can be found at \url{https://github.com/rabraker/AFM_CS}}. Experimental results are provided in Sec.
\ref{sec:results}. Finally, we provide a few concluding remarks in
Sec. \ref{sec:conclusions}.

@@

In the AFM application, the probe can only measure a single pixel at a time.
Thus the rows of $R$ are a subset of the rows of an $m$ by $m$ identity matrix.
Ideally, the sparsity basis and
the measurement matrix $R$ will have a low \textit{mutual coherence}, a
measure that describes how each of the rows of $R$ (the measurements)
``spreads out'' in the domain of $U$ \cite{candes2007sparsity}.
In the following, we assume that $U^TU=I$, though in the simulation and
experimental results, we take $U$ as the Discrete Cosine Transform (DCT) basis.
The DCT basis generally keeps a good balance between achieving a low
mutual coherence between $U$ and the $\mu$-path sensing
matrices $R$ and providing a high sparsity for typical AFM sample images.

@@

\todo{This development is way too long!}
To mitigate these affects, we propose a new variant of BPDN that we term basis pursuit with
vertical variation (BPVV). BPVV adds a vertical total variation penalty in the spatial domain to the
optimization objective. That is, \eqref{op:bp} is modified to
\todo{It has been my observation that some benefit is gained by including $D_h$, but weighting it less than $D_v$. Not sure if we should leave it in. If so, BPVV should be BPTV or something.}
\begin{align}
  \min_{x\in Q_p}~f(x) &= \min_{x\in Q_p} \left\|U^Tx\right\|_1
                         + \alpha\left\|D_vx\right\|_1
                         + \beta\left\|D_hx\right\|_1 \label{op:bp_tv}\\
                       &=\min_{x\in Q_p} \left\|W^Tx\right\|_1 \label{op:bp_tvW}
                         % \quad W = \begin{bmatrix}U&\alpha_hD^T_h&\alpha_vD^T_v \end{bmatrix}^T \nonumber
\end{align}
where
\begin{equation*}
W = \begin{bmatrix}U^T&\alpha D_h&\beta D_v \end{bmatrix}
\end{equation*}
with ${D_v x=\text{vec}(\nabla_v X)}$ (resp., ${D_v x=\text{vec}(\nabla_v X)}$) representing a 
discrete gradient of a matrix in the vertical (resp., horizontal) direction (see, e.g., \cite[Section 6.1,]{becker_nesta_2011}). 
% and
% \begin{align*}
%   (\nabla_v X)_{i,j} = 
%   \begin{cases}
%     X_{i+1,j} - X_{i,j}, & 1\leq i<h,~ 1\leq j\leq s,\\
%     0, & \phantom{:}i=h,~\phantom{:::::} 1\leq j\leq s.
%   \end{cases}\\
%   (\nabla_h X)_{i,j} = 
%   \begin{cases}
%     X_{i,j+1} - X_{i,j}, & 1\leq i\leq h,~1\leq j<s \\
%     0, & \phantom{}1\leq i\leq,~\phantom{:::} j=s
%   \end{cases}
% \end{align*}
Thus, in \eqref{op:bp_tv}, $\left \| D_v x \right \|_1$ (resp., $\left \| D_h x \right \|_1$) is the total variation (TV) of the signal in the vertical (resp., horizontal) direction.
The parameters $\alpha$ and $\beta$ are weighting parameters.
The description of BPVV in \eqref{op:bp_tvW} can be interpreted as changing our assumption of sparsity in the DCT basis to assuming sparsity in an overcomplete dictionary \cite{candes_redundant_2011}.
\todo{I believe this is correct: Sean/Yufan can you confirm or reject?}

Moreover, when written as \eqref{op:bp_tvW}, the problem is in a form that may be solved with NESTA~\cite{becker_nesta_2011}.

% For completeness, we give an overview here.
% To that end, we re-write the cost $f(x)$ in \eqref{op:bp_tvW} as
% \begin{equation*}
%   f(x) = \max_{u\in Q_d} \left\langle u, W^Tx \right\rangle,\quad Q_d = \{u:~||u||_{\infty} \leq 1\}.
% \end{equation*}

% One of the core features of the NESTA algorithm is to replace the non-smooth functional $f(x)$ with a smoothed approximation
% \begin{equation}
%   f_{\mu} = \max_{u\in Q_d} \left\langle u,
%     W^T x \right\rangle - \frac{\mu}{2}||u||_2^2. \label{eqn:fcn_prox}
% \end{equation}
% The gradient of \eqref{eqn:fcn_prox} is given by
% \begin{equation*}
%   \nabla f_{\mu}(x)[i] = Wu_{\mu}(x)
% \end{equation*}
% where
% \begin{equation*}
%   (u_{\mu}(x))[i] = 
% \begin{cases}
%     \mu^{-1}(W^Tx)[i], & |W^T x[i]| < \mu,\\
%     \text{sgn}(W^T x[i]), & \text{else}.
%   \end{cases}
% \end{equation*}
% The optimization \eqref{op:bp_tv} may now be solved using Algorithm~\ref{ag:NESTA}.

% \begin{algorithm}
%   \SetKwInOut{Initialize}{Initialize} \SetKwInOut{Output}{Output}

%   \Initialize{$x \in Q_p, \mu=0.9||W^T x_0||_{\infty}$, $L_{\mu} = \frac{1}{\mu}||W||^2_2$}
%     % $x^{k+1} = x^{k}$\\
%   \While{$\mu < \mu_{\textrm{final}}$ } {
%     $k=0$\\
%       \While{$\Delta f_{\mu} > \delta$} {
%         $\alpha_k = \frac{1}{2}(k+1)$ \\
%         $\tau_k = \frac{2}{k+3}$ \\
%         $\displaystyle y_k = \text{arg } \min_{x\in Q_p}
%           \frac{L_{\mu}}{2}||x - x_k||_2^2 + \langle \nabla f(x_k),~ x\rangle$\\
%         $\displaystyle {z_k = \text{arg } \min_{x\in Q_p} \frac{L_{\mu}}{2}||x-x_0||_2^2 +
%         \langle \sum_{i=0}^k \alpha_i \nabla f(x_i), ~x \rangle}$\\
%         $x_{k+1} = \tau_kz_k + (1-\tau_k)y_k$\\
%         $k \leftarrow k + 1$\\
%       }
%       $x_0 = x_k$\\
%       $\mu = \gamma \mu$\\
%       $L_{\mu} = (1/\mu)||W||^2_2$
%     }
%   \Output{Reconstruction $x_k$}
%   \caption{NESTA algorithm}
%   \label{ag:NESTA}
% \end{algorithm}
%   \todo{seems like a waste of space to reprint the algo, since its really no different than the reference}

% In the termination condition for the inner loop, $\Delta f_{\mu} = |f_{\mu}(x_k) - \bar{f}_{\mu}(x_k)|/\bar{f}_{\mu}(x_k)$ where
% \begin{equation}
% \bar{f}_{\mu}(x_k) = \frac{1}{\min\{10, k\}} \sum_{\ell=1}^{\min\{10,k\}} f_{\mu}(x_{k-\ell})
% \end{equation}
% When $RR^T=I$, the sub-problems in lines 6 and 7 have a closed-form solution. Details can be found in~\cite{becker_nesta_2011}.

% % The sub-problems in lines 6 and 7 have the form
% % \begin{equation}
% %   p = \textrm{arg } \min_{x\in Q_p} \frac{L}{2}||x - r|| + \langle g,~x - r\rangle
% % \end{equation}
% % for some vectors $g$ and $r$ and, as shown in~\cite{becker_nesta_2011}, have a closed-form solution given by
% % \begin{align}
% %   \lambda & = \textrm{max}(0, \sigma^{-1}\left| b - Rq\right| - L\\
% %   q &= r - L^{-1}g\\
% %   p &= \left(I - \frac{\lambda}{\lambda + L} R^TR\right)\left( \frac{\lambda}{L}R^Tb + q\right).
% % \end{align}

@@

Implementing the $\mu$-path scheme involves operating the AFM in several
distinct stages. In the $xy$-direction, the system must transition from tracking
a step command (in the transition to a new measurement location) to tracking a
scan pattern. For our simple integral controller, this only involves changing
the reference signals $x_{ref}$ and $y_{ref}$.
In the $z$-direction, the system
must transition between tip descent, surface scanning, tip retraction, and
maintaining a $z$-axis position.

\begin{figure*}[ht!]
  \centering
  \includegraphics[width=1\textwidth]{figures/AFM_loop_xyz.pdf}
  \caption{Block diagram of the $Z$-axis control loop. The anti-windup is active
    for decision index $i\in\{0,1,5\}$, which correspond to states such that
    $r_Z=\rzup$.}
  \label{fig:afm_bd_dinv}
\end{figure*}
\subsection{The pre-scan}
% \begin{figure*}
%   \begin{subfigure}{.33\textwidth}
%     \includesvg[width=1\textwidth]{figures/zbounce_uz_example.svg}
%     \caption{ }
%     % \label{fig: }
%   \end{subfigure}
%   \begin{subfigure}{.33\textwidth}
%     \includesvg[width=1\textwidth]{figures/prescan_uz_example.svg}
%     \caption{ }
%     \label{fig:uz_prescan}
%   \end{subfigure}
%   \begin{subfigure}{.33\textwidth}
%     \includesvg[width=1\textwidth]{figures/prescan_zbounce_PSD.svg}
%     \caption{ }
%     % \label{fig: }
%   \end{subfigure}
%   \caption{(a) A ``$Z$-bounce'' experiment where the $XY$-stage is motionless
%     and the cantilever is repeatedly engaged and disengaged. (b) One cycle of a
%     tightly packed set of CS-cycles where the movement between each measurement
%     location is 0. (c) PSDs from the portions of the trajectories which are
%     colored blue and turquoise, averaged over many such cycles, demonstrating
%     that the scan process itself reduces vibration in the $Z$-axis.}
%   \label{fig:prescan_difference}
% \end{figure*}
After the tip-descent, we begin scanning in a ``pre-scan'' phase (state (3)).
During this phase,

\subsection{Control}\label{sec:control}
\begin{figure}
  \centering
  \includesvg[width=1\columnwidth]{figures/z_control_design.svg}
  \caption{FRFs of the $Z$-axis. The blue curve is the open loop response from $u_Z$ to deflection. By inverting the bending mode at 215~Hz, we achieve the black curve in closed-loop.}
  \label{fig:z_control}
\end{figure}

The control structure for each axis is similar and essentially consists of a set of filters in series with a PI controller. The open-loop frequency response for the $Z$-axis is shown in Fig.~\ref{fig:z_control} (black curve) and in Fig.~\ref{fig:mimo_frf_uxuy} for the $X$ and $Y$ axes (red curves). The first resonance of each axis is the bending mode. For the $Z$ axis, this resonance is at 215~Hz and at approximately 350~Hz for the $X$ and $Y$ axes.

@@

@@

@@

For raster scanning, we use a truncated Fourier series, where each Fourier coefficient is scaled by the inverse of the closed-loop FRF at the corresponding frequency. We truncate this series such that the highest frequency is smaller than 200 Hz. See, e.g., \cite{clayton_review_2009} for more details on this strategy. Note that this scheme implies that the effective bandwidth of the $X$-axis controller is higher while raster scanning than while CS-scanning. On the other hand, it also implies that the for faster scan rates, fewer Fourier coefficients are used, and so the approximation to a triangle wave is worse.
\begin{figure}
  \includesvg[width=1\columnwidth]{figures/with_wo_ff.svg}
  \caption{Scans over mica. (left) Without feedforward. (right) with feedforward.}
  \label{fig:with_ff}
\end{figure}

@@

\begin{figure}[t!]
  \includesvg[width=1\columnwidth]{figures/cs_raster_pixel_rows_6-5-2019.svg}
  \caption{Rows of pixels, as indicated by the red lines in
    Fig.~\ref{fig:resultsF1_images}. For clarity, not all images are included.}
  \label{fig:pixel_rows}
\end{figure}
